Energy Dependent X-Ray Rim Widths in Tycho's Supernova Remnant

### 2014-09-13 manuscript/paper-tycho.tex
Kepler regions, Tycho tables & avg fwhms/errs
First round of Kepler region picks. Generate more Tycho fit tables and
compute averaged FWHMs/errors for fits. Update code to fit with only 1
free param (B0 xor eta2).  Fix misc. bugs, more work on paper

% \documentclass[manuscript]{aastex}  % one-column, double-spaced
% \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
% \documentclass[iop, apj, numberedappendix]{emulateapj}

@@

\usepackage{amsmath}  % amsthm, amssymb
\usepackage{hyperref}
% \usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
\usepackage{booktabs}
%\usepackage[labelfont=bf, labelsep=period]{caption}  % Custom float captions
%\usepackage{pdflscape}  % rotate pages (Texlive)

\newcommand{\mt}{\mathrm}
\newcommand{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
\newcommand{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
\newcommand{\ptl}{\partial}
\newcommand{\del}{\nabla}

% This paper
\newcommand{\tsup}{\textsuperscript}
\newcommand{\Chandra}{\textit{Chandra}\ }
\defcitealias{ressler2014}{R14}

@@

We first briefly review the models we consider for particle transport; a fuller
exposition is given by \citetalias{ressler2014}.

Just present the governing transport equations.  From:
\[
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\]
we obtain (1-D time-independent flow, neglect compressible flow?!,
space-independent diffusion coefficient):
\[
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C
\]
and by selection of the source/sink term $C$ we obtain either a
simplified model:
\begin{equation} \label{eq:simp-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
where this is equation (6) of \citetalias{ressler2014}; we also look at
\begin{equation} \label{eq:full-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.

@@

@@

We obtained radial intensity profiles by integrating along the shock in each
region.  Intensity profiles peak sharply at/behind the shock, demarcating our
thin rims, \note[Aaron]{abt 2--3 arcsec; measure this or report $w_u$?}
and then fall off until thermal emission from ejecta picks up at Tycho's
``contact discontinuity'' \citep{warren2005}.

We fit rim profiles, obtained by integrating intensity along the shock in each
region, to a piecewise two-exponential model:
\begin{equation} \label{eq:prof}
    h(x) =
    \begin{cases}
        A_u \exp \left(\frac{x_0 - x}{w_u}\right) + C_u, &x \geq x_0 \\
        A_d \exp \left(\frac{x - x_0}{w_d}\right) + C_d, &x < x_0
    \end{cases}
\end{equation}
where $h(x)$ is profile height and $x$ is radial distance from remnant center.
The rim model, which we emphasize is strictly empirical, has 6 free parameters
$A_u, x_0, w_u, w_d, C_u, C_d$ with $A_d = A_u + (C_u - C_d)$ enforcing
continuity at $x=x_0$. Our model is similar to that of \citet{bamba2003,
bamba2005-hist} and differs slightly from that of \citetalias{ressler2014}.
To fit only the nonthermal rim in each intensity profile, we smoothed profiles
with a 21-point ($\abt 10\arcsec$) Hanning window and bounded the fit
domain at the first local data minimum downstream of rim peak; the fit domain
extends upstream to the region's outer edge.

@@

To estimate FWHM uncertainties, we horizontally stretched each best-fit
profile by mapping radial coordinate $x$ to
$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x))$ with $\xi$ an arbitrary stretching
parameter; this yields a new profile $h'(x) = h(x'(x))$.
We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7,
yielding confidence limits on our measured FWHMs.

@@

TODO?! We also fit the spectra to absorbed power law models with 1 and 2
additional Gaussian components for \ion{Si}{13} and \ion{S}{15} He$\alpha$
lines at $\abt 1.8$, $2.4$ keV.  We compute some equivalent width, or compare
the goodness-of-fit with and without the additional lines, to rule out the
presence of a line (but, cf. \citet{protassov2002} on line detection
statistics!).

@@

A few remnant-specific parameters enter into the model calculations.  We take
electron spectral index $s = 2.3$ (from radio spectral index $\alpha = 0.65$,
\citet{kothes2006} \note[Aaron]{not using $0.58$ from Green's catalog?!}),
remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
\citep{green2009}.  Tycho's forward shock velocity varies azimuthally by up to
a factor of 2; we interpolate the data of \citet{williams2013} to estimate
individual shock velocities for each of our regions.

@@

We give figures and tables with rim profile fit information.

@@

\begin{table*}[h]
\scriptsize
\centering
\caption{Filament 2 full width at half max measurements.
Exponent $m_E$ estimated point to point.\label{tab:flmt2}}
\input{tab-fwhms.tex}
\tablecomments{Mean FWHMs computed by arithmetic mean, errors from blah}
\end{table*}

@@

Here are some fit results for a subset of regions, just those contained in
Filament 1 (Table~\ref{tab:fit}).  Errors are estimated by 
Explain error values on parameters

\begin{table*}
\scriptsize
\centering
\caption{Full model best fit parameters, Filament 1.
    \label{tab:fit}}
\input{tab-fits-flmt1.tex}
\end{table*}

Table~\ref{tab:fit-avg-fwhm} shows best fits to averaged FWHMs (averaged FWHMs
not shown).  For FWHM errors, I use the standard error of the mean (with some
minor nuances; I am using sample standard deviation).

\begin{table*}
\scriptsize
\centering
\caption{Full model best fit parameters for filament-averaged FWHMs.
    \label{tab:fit-avg-fwhm}}
\input{tab-fits-avg.tex}
\end{table*}

Finally, Table~\ref{tab:fit-avg-par} shows averaged best-fit parameters for
Filament 1 only, at this time.  The parameter errors are standard errors from
the averaging process and may reflect the presence of outliers.

\begin{table*}
\scriptsize
\centering
\caption{Average of best-fit parameters for individual regions
    \label{tab:fit-avg-par}}
\input{tab-fits-par-avg.tex}
\end{table*}

\begin{table*}
\scriptsize
\centering
\caption{Full model best fit parameters, Filament ??, with $\eta_2 = 1$ fixed}
%    \label{tab:fit-avg-par}}
%\input{tab-fits-par-avg.tex}
Coming soon...
\end{table*}

@@

\begin{table}[h]
\scriptsize
\centering
\caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}}
\label{tab:sean}
\input{tab-sean.tex}
\end{table}

\begin{table*}[h]
\scriptsize
\centering
\caption{SN 1006 best fit parameters, 2 highest energy bands (full model)}
\label{tab:sn1006-2band}
\input{tab-sn1006-2band.tex}
\end{table*}

\begin{table*}[h]
\scriptsize
\centering
\caption{SN 1006 best fit parameters, 3 energy bands (full model)}
\label{tab:sn1006-3band}
\input{tab-sn1006-3band.tex}
\end{table*}

@@

\begin{table}[h]
\tiny
\centering
\caption{Best fit parameters for the filaments of Cas A based on data from
Araya et. al (2010) in varying values of $\mu$ (Approximate Analytic Results)
Dashes denote places where fits were unobtainable.}
\label{tab:araya}
\input{tab-sean-casA.tex}
\end{table}

>>>>

% \documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
% \documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
% \documentclass[iop, apj, numberedappendix]{emulateapj}

@@

\usepackage{amsmath}  % amsthm, amssymb
% \usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
\usepackage{booktabs}
%\usepackage[labelfont=bf, labelsep=period]{caption}  % Custom float captions
%\usepackage{pdflscape}  % rotate pages (Texlive)
\usepackage{hyperref}

\newcommand*{\mt}{\mathrm}
\newcommand*{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
\newcommand*{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
\newcommand*{\ptl}{\partial}
\newcommand*{\del}{\nabla}

% This paper
\newcommand*{\tsup}{\textsuperscript}
\newcommand*{\Chandra}{\textit{Chandra}\ }
\newcommand*\mean[1]{\bar{#1}}
\defcitealias{ressler2014}{R14}

@@

We briefly review our particle transport models and relevant equations for our
modeling; a fuller review and exposition is given by \citetalias{ressler2014}.
\note[Aaron]{is it necessary to give Sean's equation numbers?  How many of the
derived equations should we give?}

\note[Aaron]{Double check against Rettig/Pohl}
The electron distribution which gives rise to the observed synchrotron
radiation is injected at the forward shock and transported by advection
and plasma diffusion, following the advection-diffusion equation:
\[
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\]
we obtain (1-D time-independent flow, neglect compressible flow?!,
space-independent diffusion coefficient (did we neglect the spherical
coordinate terms?)):
\[
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C
\]
and by selection of the source/sink term $C$ we obtain either a
simplified model:
\begin{equation} \label{eq:simp-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
where this is equation (5) of \citetalias{ressler2014}; we also look at
\begin{equation} \label{eq:full-mod}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.

@@

\subsection{Energy dependent widths, diffusion}

\begin{itemize}
    \item Bohm diffusion: $D(E) = \eta C_d E / B$
    \item Generalized diffusion: $D(E) = \eta C_d E^\mu / B = \eta_h D(E_h)
        (E/E_h)^\mu$
\end{itemize}

Explain the use of fiducial energy -- this makes sense and eases discussion,
but linking $E_h$ and $\eta_2$ to $\eta$ and plain Bohm diffusion seems a bit
murky to me.

For the simple model, we have equation (6) of \citetalias{ressler2014}:
\[
    a = \frac{2 D / v_d}{ \sqrt{ 1 + \frac{4D}{v_d^2 \tau_{\mt{synch}}}} - 1}
\]
which we relate to full width half max by projection factor $\beta = 4.6$
so that $w = \beta a$, assuming (1) electron distribution exponential in radial
coordinate $x$, and (2) spherical source \note[Aaron]{shell?}
\citep{ballet2006}.

For the full model (equation~\eqref{eq:full-mod}), we numerically solve for
electron distribution $f(E,x)$ using solutions due to \citet{lerche1980} and
\citet{rettig2012};

\subsection{Tycho parameters}

Give numbers ($v_s$, $v_d$, $r_s$, etc.).  Give a definition of the cut-off
energy following Rettig and Pohl (again cite Sean's paper).
We use an electron spectrum cut-off energy of:
\[
    E_{\mt{cut}} =
        \left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)}
        \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
    \left[
        \frac{E_h^{\mu - 1}}{\eta}
    \right]^{1 / (1 + \mu)}
\]
which is equation~(19) of \citetalias{ressler2014}.
\note[Aaron]{This differs from Sean's presentation -- I drew this from the
Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
$E_h$ ?!  Come back to this shortly.}

@@

We obtained radial intensity profiles by integrating along the shock in each
region.  Plotted and fitted profiles are reported in vignetting and
exposure-corrected \note[Aaron]{double check CIAO guides} intensity units;
error bars are computed from raw count data assuming Poisson statistics.
Intensity profiles peak sharply at/behind the shock, demarcating our
thin rims, \note[Aaron]{abt 2--3 arcsec; measure this or report $w_u$?}
and then fall off until thermal emission from ejecta picks up at Tycho's
``contact discontinuity'' \citep{warren2005}.

We fitted rim profiles, obtained by integrating intensity along the shock in
each region, to a piecewise two-exponential model:
\begin{equation} \label{eq:prof}
    h(x) =
    \begin{cases}
        A_u \exp \left(\frac{x_0 - x}{w_u}\right) + C_u, &x \geq x_0 \\
        A_d \exp \left(\frac{x - x_0}{w_d}\right) + C_d, &x < x_0
    \end{cases}
\end{equation}
where $h(x)$ is profile height and $x$ is radial distance from remnant center.
The rim model, which we emphasize is strictly empirical, has 6 free parameters
$A_u, x_0, w_u, w_d, C_u, C_d$ with $A_d = A_u + (C_u - C_d)$ enforcing
continuity at $x=x_0$. Our model is similar to that of \citet{bamba2003,
bamba2005-hist} and differs slightly from that of \citetalias{ressler2014}.
To fit only the nonthermal rim in each intensity profile, we smoothed profiles
with a 21-point ($\abt 10\arcsec$) Hanning window and bounded the fit
domain at the first local data minimum downstream of rim peak; the fit domain
extends upstream to the region's outer edge.

@@

To estimate FWHM uncertainties, we horizontally stretched each best-fit
profile by mapping radial coordinate $x$ to
$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x))$ with $\xi$ an arbitrary stretching
parameter; this yields a new profile $h'(x) = h(x'(x))$.
We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7
and the stretched or compressed FWHMs as upper/lower bounds on our reported
FWHMs.

Finally, we took a geometric average of rim widths $w_i(E)$ in each filament,
with $i$ indexing each region, as
\[
    \mean{w}(E) = \left( \prod_{i=1}^{n} w_i(E) \right)^{1/n}
\]
Why?  My (Aaron's) justification:
\begin{itemize}
\item Arithmetic mean width is not representative of a filament's
    spatially varying width (in practice, projected rim emission likely
    does not arise from a spherical shell \citep[c.f.][]{hester1987}).
    Our measurements aren't randomly distributed.
\item I assume / guess that $m_E$ is more likely to be constant over a
    filament length.  Intuitively, I think of $m_E$ being a proxy for the
    relative strength of transport mechanisms, as opposed to being a function
    of the absolute strengths of two mechanisms.  But that's not rigorous,
    and it doesn't seem obvious $m_E$ should be more robust than width $w$
    over a filament's length (since we're taking a first derivative, which
    is usually more painful?).
\item The geometric mean of FWHMs gives an arithmetic mean of ``sampled''
    $m_E$ values by definition.  To show this explicitly (just a sanity check)
    from the equation $w(E) = \alpha E^{m_E}$, where $\alpha$ is a throwaway
    constant, we have $m_E = \ln(w(E)/\alpha) / \ln(E)$.  Then, $m_E$ computed
    from geometric mean width $\mean{w}(E)$ is:
    \begin{align*}
        \mean{m_E}(E)
            &= \frac{\ln\left[ \mean{w}(E) \right] - \ln\alpha}{\ln(E)} \\
            &= \frac{\ln\left[ \left( \prod_{i=1}^{n} w_i(E) \right)^{1/n}
                        \right] - \ln\alpha}{\ln(E)} \\
            &= \frac{\frac{1}{n}\left(
                         \sum_{i=1}^{n} \ln\left[w_i(E)\right]
                     \right) - \ln\alpha}{\ln(E)} \\
            &= \frac{\frac{1}{n} \sum_{i=1}^{n}
                     \left( \ln\left[w_i(E)\right] - \ln\alpha \right)}
                    {\ln(E)} \\
            &= \sum_{i=1}^{n} (m_E)_i (E)
    \end{align*}
    Or, we could just say that we're taking an arithmetic mean of
    $\ln(w_i(E))$.
\item The geometric mean is less sensitive to outliers than the arithmetic
    mean -- but this may not necessarily be desirable, if it hides
    real measurement signal.
\end{itemize}
The counterpoints are that (1) in practice, it may not make much difference
(especially as we only have sample size about $1$--$5$ at best), variations
from changing up calculations are hard to distinguish from plain old
measurement spread; (2) arithmetic mean is simpler to understand; (3)
assumption of roughly constant widths does not look terrible in Tycho -- but I
have not investigated this... (clearly, rims fade at edges, but at bright
center regions do they swell or vary in width?).

Errors were computed by taking standard errors on $\log w(E)$
(i.e., $\sigma(w(E)) / \sqrt(n)$, as the CLT applies in log space) and then
converting back to physical parameter space.  These errors are asymmetric; we
take the maximum error in either direction as error on our FWHMs for all fits
(but we report the asymmetric error otherwise).
\textbf{WARNING:} this procedure is incomplete.  Because our sample sizes are
tiny (typically, $n \sim 2$), to obtain a true 68.3\% confidence interval /
1-sigma error, we should compute error from the Student's $t$-distribution.
The net result is that our errors should be doubled in most cases.
\emph{I have not yet applied this correction.}

Some problems:
\begin{itemize}
    \item Errors are very large, as currently calculated -- they reflect the
        assumption that $m_E$ is normally distributed, and give a statistical
        uncertainty on population mean $m_E$.
        (or if we used the arithmetic mean, same problem for FWHMs)
        This throws out our very small width errors, and we want to take
        advantage of our nice photon statistics.
    \item Since geometric mean is strictly lower than arithmetic mean,
        this will bias our parameter values downwards -- it's not clear which
        approach would give more ``correct'' estimates
\end{itemize}

One approach may be to slice up the regions more thinly and accept a bit more
uncertainty in FWHM values.  This would make it eaiser to either (1) compute
fits to regions individually (then, errors are set by profile fitting
uncertainty alone -- I think our estimates are still a little too small, and we
should be using 1-sigma errors rather than 90\% CIs), and (2) average many
FWHMs, in whatever way, and get more robust / lower error filament values.

@@

Background spectra were extracted from circular regions around the remnant's
exterior; we matched each selected rim region to the nearest background region
and subtracted the background spectrum accordingly. \note[Aaron]{rewrite for
concision/clarity}.

\note[Aaron]{TODO?!} We also fit the spectra to absorbed power law models with
1 and 2 additional Gaussian components for \ion{Si}{13} and
\ion{S}{15} He$\alpha$ lines \note[Aaron]{?? I think I got this from AtomDB but
not certain of details} at $\abt 1.8$, $2.4$ keV.
We compute some equivalent width, or compare the goodness-of-fit with and
without the additional lines, to rule out the presence of a line
(but cf. \citet{protassov2002} on line detection statistics!).

@@

A few remnant-specific parameters enter into the model calculations.  We take
electron spectral index $s = 2.3$ (from radio spectral index $\alpha = 0.65$,
\citet{kothes2006} \note[Aaron]{not using $0.58$ from Green's catalog?!}),
remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
a factor of 2; we interpolate the data of \citet{williams2013} to estimate
individual shock velocities for each of our regions.

@@

To perform fits, we took a geometric average of rim widths in each energy band,
for each filament; 
For FWHM errors, I use the standard error of the mean (with some
minor nuances; I am using sample standard deviation).
PUT IN METHODS SECTION

This contrasts with taking an arithmetic average of the rim widths.  The
geometric average does not represent the expected value of FWHM measurements,
along the rim.  However, filaments should vary in width along their lengths in
response to

A key question is whether we wish to report an average w/ errors, corresponding
to our specific measurements (if we alter our profile fit function, or take a
new observation of Tycho with different counts, how will our measurement
change) -- or, if we wish to report an average w/ error that estimates the
population spread -- if we have huge resolution / collecting power, and could
slice up the filament in many locations and sample its FWHMs very well, what
would be the population spread on that sample?

If the FWHMs vary systematically within the filament -- an estimate of
population spread will give errors that are too large.

We might expect the FWHM energy dependence (our $m_E$) to be consistent across
the filament, as opposed to the actual FWHM lengths.
If we expect the FWHM energy dependence

But, both values are important -- the FWHM lengths tell us about the magnetic
field strength

In Table~\ref{tab:flmt2} we report averaged widths (data and fits for
individual filaments are given in \emph{appendix, supplement?}).

@@

\begin{table*}
\scriptsize
\centering
\caption{Filament 2 full width at half max measurements.
Exponent $m_E$ estimated point to point.\label{tab:flmt2}}
\input{tab-fwhms.tex}
\tablecomments{Mean FWHMs computed by arithmetic mean, errors from blah}
\end{table*}

@@

\subsubsection{Individual regions}

First, Table~\ref{tab:fits-flmt1} presents full model fit results for the regions
contained in Filament 1.  As currently presented (preliminary results), errors
are computed by varying free parameters $B_0$, $\eta_2$ to obtain a
$\Delta\chi^2 = 1$, corresponding to $1$-$\sigma$ confidence limits on our fit
parameters.

\begin{table*}[ht]
\scriptsize
\centering
\caption{Full model best fits for individual regions, Filament 1.
\label{tab:fits-flmt1}}
\input{tab-fits-flmt1.tex}
\end{table*}

\subsubsection{Combining regions, in various ways}

Now, we present fit results for averaged filament FWHMs, for sanity's sake.
Table~\ref{tab:fits-avg} presents full model fits to arithmetic average of
FWHMs in each filament.  The model fit predictions for each filament are
plotted in Figure~\ref{fig:fits-avg}.

\begin{table*}
\scriptsize
\centering
\caption{Best fits for each filament's averaged FWHMs.
\label{tab:fits-avg}}
\input{tab-fits-avg.tex}
\end{table*}

\begin{figure}
\centering
\plottwo{figures/f0-fits-avg-flmt1.png}{figures/f0-fits-avg-flmt2.png} \\
\plottwo{figures/f0-fits-avg-flmt3.png}{figures/f0-fits-avg-flmt4.png} \\
\includegraphics[width=0.25\textwidth]{figures/f0-fits-avg-flmt5.png}
\caption{Plots of best-fits to averaged FWHMs.\note[Aaron]{Update plots
for better subplot display in final version, if we want to keep these}}
\label{fig:fits-avg}
\end{figure}

Finally, Table~\ref{tab:fits-par-avg} shows averaged best-fit parameters.
Parameter errors are standard errors from averaging and may reflect the
presence of outliers (especially as the sample number is $1$--$5$).

\begin{table*}
\scriptsize
\centering
\caption{Filament-wide average of best-fit parameters for constituent regions.
\label{tab:fits-par-avg}}
\input{tab-fits-par-avg.tex}
\end{table*}

We also computed best fits while holding $\eta_2 = 1$; i.e., requiring Bohm
diffusion at $2 \unit{keV}$.  The results (Table~\ref{tab:fits-avg-eta2-fix})
are relatively insensitive to $\mu$.

\begin{table*}
\scriptsize
\centering
\caption{Best fits with $\eta_2 = 1$ fixed, for filament averaged FWHMs.
\label{tab:fits-avg-eta2-fix}}
\input{tab-fits-avg-eta2-fix.tex}
\end{table*}

\subsubsection{How confidently can we reject B-damping?}

Everything hinges on our error bars -- this is most important.  Our rims do
thin consistently, in most regions (might be one or two places where they
don't), but (1) the errors in our individual FWHMs are larger than I'm
currently reporting because different profile fits will give a larger spread of
FWHMs (might need to consider reduced chi-squared here, but using chi-sqr to
select profile fit models is not physically meaningful)

@@

\begin{table}[h]
\scriptsize
\centering
\caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}.
\label{tab:sean}}
\input{tab-sean.tex}
\end{table}

\begin{table*}[h]
\scriptsize
\centering
\caption{SN 1006 best fit parameters, 2 highest energy bands (full model).
\label{tab:sn1006-2band}}
\input{tab-sn1006-2band.tex}
\end{table*}

\begin{table*}[h]
\scriptsize
\centering
\caption{SN 1006 best fit parameters, 3 energy bands (full model).
\label{tab:sn1006-3band}}
\input{tab-sn1006-3band.tex}
\end{table*}

@@

\begin{table}[h]
\tiny
\centering
\caption{Best fit parameters for the filaments of Cas A based on data from
Araya et. al (2010) in varying values of $\mu$ (Approximate Analytic Results)
Dashes denote places where fits were unobtainable.
\label{tab:araya}}
\input{tab-sean-casA.tex}
\end{table}
